---
title: "Dissertaion Progress Report"
author: "Lin Chen"
date: "`r (Sys.time())`"
output:
  # html_document: default
   pdf_document: default
  # word_document: default
---

<!-- load R sources -->
``` {r echo=FALSE, results="hide"}
knitr::opts_chunk$set(error=FALSE)
library("knitr")
library("kableExtra")
source("R/clean.R")
source("R/analysis.R")
```

### Survey Information
* Survey date: 03/06 – 06/06
* Survey site: WeChat
* Sampling method: Snowball
* Reached: 1587 (7 provincial level district in China)
* Returned: 247 (189 participants are from Anhui Province where the survey started to circulate in WeChat networks)
* Effective sample: 225
* Mean survey completion time: 14mins, 27seconds


<!-- Prepare data for analysis -->
```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
src <- "data/2157154_seg_1.csv" 
coding <- read.csv("data/survey_questions.csv", stringsAsFactors = FALSE)
dat0 <- read_dat(src, coding)
dat0 <- tran_age(dat0)
dat0 <- tran_other(dat0)
```

### Internal consistency measures of reliability
```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
dat <- sub_scale(dat0, coding, remove = FALSE)

### cronbach's alpha from psych package
#status origin - 0.916 - excelllent
cols <- grep("status_origin[0-9]{1}", names(dat))
a_1 <- psych::alpha(dat[cols])$total$std.alpha

#status current - 0.917 - excellent
cols <- grep("status_current[0-9]{1}", names(dat))
a_2 <- psych::alpha(dat[cols])$total$std.alpha

# #con-2-child - can become a subscale
# psych::alpha(dat[29:34])$total$std.alpha
# # pro-2-child - can become a subscale
# psych::alpha(dat[36:41])$total$std.alpha
#motherhood experience - questionable, but this is not a subscale though
# cols <- grep("motherhood[0-9]{1}", names(dat))
# psych::alpha(dat[cols])$total$std.alpha
# life satisfaction - 0.886 - great
cols <- grep("life_satisfaction[0-9]{1}", names(dat))
a_3 <- psych::alpha(dat[cols])$total$std.alpha
# motherhood satisfaction - 0.835 - great
cols <- grep("motherhood_satisfaction[0-9]{1}", names(dat))
a_4 <- psych::alpha(dat[cols])$total$std.alpha
# mother interferes work - 0.932 - excellent
cols <- grep("mother_interferes_work[0-9]{1}", names(dat))
a_5 <- psych::alpha(dat[cols])$total$std.alpha
# work interferes mother - 0.951 - excellent
cols <- grep("work_interferes_mother[0-9]{1}", names(dat))
a_6 <- psych::alpha(dat[cols])$total$std.alpha

```

The questionnaire has six sub-scales. For each of the sub-scales, Cronbach's alpha is used to test its reliability. Below are the sub-scales and their reliability scores.

* 1) mother's status in original family (alpha = `r round(a_1, 2)`)
* 2) mother's status in current family (alpha = `r round(a_2, 2)`)
* 3) life satisfaction (alpha = `r round(a_3, 2)`)
* 4) motherhood satisfaction (alpha = `r round(a_4, 2)`)
* 5) motherhood interfers work (alpha = `r round(a_5, 2)`)
* 6) work interferes motherhood (alpha = `r round(a_6, 2)`)

In general, Cronbach's alpha indicates great/excellent reliability.


### .2.content analysis of motherhood perception
```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
dat <- sub_scale(dat0, coding, remove = TRUE)
dat <- content_anlaysis(dat)
```
The questionnaire asks mothers to provide theri own perceptions of motherhood. A content analysis has been undertaken. Two types of codes - modern and traditional mothers are constructed, along with corresponding sets of sub-codes. (should I say the sources of the codes? traditional is from https://baike.baidu.com/item/%E4%B8%AD%E5%8D%8E%E6%AF%8D%E4%BA%B2%E6%96%87%E5%8C%96%E5%A4%8D%E5%85%B4%E5%B7%A5%E7%A8%8B/19483382 , and modern is from the content itself.)


### two sample t test
```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
# group by whether mothers are only-children to their own parents
# we find group difference in the following variables
dat <- sub_scale(dat0, coding, remove = TRUE)
dat$high_edu <- dat$education > 2
dat$high_income <- dat$income > 1
groups <- c("only_child", "has_brothers","one_child", "young_mother", 
            "self_2_child", "high_edu", "high_income")

lapply(groups, function(group) unlist(lapply(names(dat)[-c(1:3)], function(i) two_sample_t(i, group, dat))))
```



<!-- ### Exploratory factor analysis -->
<!-- ```{r, echo = TRUE, results = 'markup'} -->
<!-- ## have to remove 2 rols to avoid singularity -->
<!-- d <- dat[-c(1:3)] -->
<!-- dat$rank2_son <- NULL -->
<!-- dat$rank_daughter <- NULL -->

<!-- for(v in names(d)) { -->
<!--   #if( !all(is.numeric(d[[v]]) & is.finite(d[[v]])) ) { -->
<!--   if( !all(is.finite(d[[v]])) ) { -->
<!--     d[[v]] <- NULL -->
<!--   } -->
<!-- } -->
<!-- d <- d[c(1:6, 23:34)] -->

<!-- ## correlation matrix -->
<!-- cor(d, method = c("pearson", "kendall", "spearman")) -->

<!-- ## principle component -->
<!-- d.pca <- princomp(d) -->
<!-- summary(d.pca) -->
<!-- plot(d.pca) # scree plot -->
<!-- #biplot(princomp(d)) -->
<!-- ## ggplot -->
<!-- g <- ggbiplot(d.pca, choices = c(1,2), obs.scale = 1, var.scale = 1,  -->
<!--               ellipse = TRUE, groups = d$only_child, -->
<!--               circle = TRUE) -->
<!-- g <- g + scale_color_discrete(name = '') -->
<!-- g <- g + theme(legend.direction = 'horizontal',  -->
<!--                legend.position = 'top') -->
<!-- print(g) -->

<!-- d.fac <- factanal(d, factors = 6, rotation = "varimax", scores=c("regression")) -->
<!-- print(d.fac, digits = 2, cutoff = .4, sort = TRUE) -->
<!-- ``` -->


