---
title: "Chapter 4 Exercises"
author: "Jumping Rivers"
output: html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 4 Exercises}
-->

```{r echo=FALSE, message=FALSE}
library("jrShiny")
library("shiny")
library("flexdashboard")
```

## Exercise 1

  * Create a R markdown document with a standard YAML header. 
    * In the main part of the document, have some R code that creates a simple
    scatter plot and saves the resulting plot as a pdf file,e.g. 
        ```{r eval=FALSE}
        x = rnorm(10)
        plot(x)
        pdf("fileA.pdf")
        plot(x)
        dev.off()
        ```
  * Now in the YAML section, add a parameter called `filename` with the value `file1.pdf`
  * In the main part of the document, access the parameter via `params$filename`
  * Instead of `fileA.pdf`, pass the parameter from the YAML header
    * Your R markdown document should display the scatter plot __and__ save the plot
    in a file called `file1.pdf`
    
## Exercise 2

  * Copy your previous Rmd file, but delete the `params` section from the YAML header
  * Pass the `filename` parameter via the `render()` function
    ```{r, eval=FALSE}
    rmarkdown::render("MyDocument.Rmd", 
	    params = list(
		  filename = "file2.pdf"
	   )
    )
    ```
  * Check that you have created `file2.pdf`

## Exercise 3

Unfortunately, to run scheduler tasks it depends on 

 * Your operating system
 * The requirement for admin privilages
 
This means it's hard to get an exercise that will suit everyone. To get the
general idea across I've created a simple function called `scheduler()`. 

When we run the same script multiple times, there are two possibilities:

  * We constantly overwrite the previous output (this is straightforward)
  * We dynamically create file names so we have a record. This is what we'll do 
  in the tasks below.
  
### Task 1

Create a standard Rmd file (don't worry about `params`). In the body of the document
include
```{r eval=FALSE}
x = rnorm(10)
plot(x)
pdf("fileA.pdf")
plot(x)
dev.off()
```
We want to change `fileA.pdf` to be unique. The easiest way is to use current time.
In R we have
```{r}
Sys.Date()
Sys.time()
```
In this exercise we'll use `Sys.time()`, but you may find `Sys.Date()` more suitable in general.
We need to convert the time to a file name. First convert it to a character

```{r}
fname = as.character(Sys.time())
```

Then add on a `pdf` file extension using the `paste0()` function

```{r}
fname = paste0(as.character(Sys.time()), ".pdf")
```
Now change `fileA.pdf` to use fname. Run your script and ensure that it works.

### Task 2

The `scheduler()` function is simple. It has three arguments:

  * `rmd_name`: The name of `Rmd` script you want to generate
  * `repeats`: How often should we run the script (from now)
  * `time_between`: The time between script calls

```{r, eval=FALSE}
library(jrShiny)
## time_between is in seconds
scheduler(script_name = "my_script.Rmd", repeats = 5, time_between = 5) 
```

Using the `schedular()` function, run your `Rmd` file 5 times with a 3 second interval.


### Handy functions for file manipulation

Function name | Description
--------------|------------
`dir.create()` | Creates a new directory
`dir.exists()` | Checks a directory exists
`file.create()` | Creates a new file
`file.exists()` | Checks a file exists
`file.remove()` | Removes a file
`file.info()` | Size, creation date, etc.











